\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}

\usepackage{geometry}
\geometry{portrait, margin=1.5in}

\begin{document}


\section*{Excercise 1}
Each class we split into several subclasses will have one single responsibility. \\
Game:
\begin{itemize}
\item Controller: this interface class will provide template for the Controller classes of different game elements. 
\begin{itemize}
\item UnitController: this abstract class has the responsibility of controlling the non moving units in the game
\begin{itemize}
\item ExplosionController: this class is responsible for modifying the explosions in the game.
\item BarricadeController: this class is responsible for modifying the barricades in the game.
\end{itemize}
\item MovingUnitController: this abstract class is a class that has the responsibility of controlling the moving units in the game. 
\begin{itemize}
	\item AlienController: this class has the responsibility of modifying the aliens in the game.
	\item SpaceShipController: this class is responsible for modifying the spaceship.
	\item BulletController: this class is responsible for modifying the bullets in the game.
	\begin{itemize}
		\item AlienBulletController this class is responsible for modifying the alienbullets in the game.
		\item SpaceShipBulletController this class is responsible for modifying th spaceshipbullets in the game.
	\end{itemize}
\end{itemize}
\end{itemize}
\end{itemize}
GameUIController, draw:
\begin{itemize}
	\item DrawUnit: this abstract class is responsible for drawing units on the screen.
	\begin{itemize}
		\item DrawAlien: this class is responsible for drawing the aliens on the screen.
		\item DrawSpaceShip: this class is responsible for drawing the spaceship on the screen.
		\item DrawBarricade: this class is responsible for drawing the barricades on the screen.
		\item DrawExplosion: this class is responsible for drawing the explosions on the screen.
		\item DrawBullet: this class is responsible for drawing the bullets on the screen.
	\end{itemize}
	\item DrawScore: this class is responsible the score on the screen.
	\item DrawLives: this class is responsible the lives on the screen.
\end{itemize}
\begin{itemize}
\item Unit: the main class of all units.
\begin{itemize}
\item MovingUnit: the main class of all units that are moving.
\begin{itemize}
\item Alien: this class is the alien unit in the game.
\item SpaceShip: this class is responsible for the spaceship unit.
\item Bullet: this class is responsible for the bullet unit.
\begin{itemize}
\item SpaceShipBullet: this class is responsible for the spaceshipbullet unit.
\item AlienBullet: this class is responsible for the alienbullet unit.
\end{itemize}
\end{itemize}
\item Explosion: this class is responsible for the explosion unit.
\item Barricade: this class is responsible for the barricade unit.
\end{itemize}
\end{itemize}


\end{document}