\section{Local co-op Multiplayer Functional Requirements}

A list of functional requirements considered for the implementation of local co-op multiplayer using the MoSCoW method described in the previous section.

\subsection{Must Haves}
The local co-op multiplayer must meet the following requirements:
\begin{itemize}
	\item A multiplayer game shall contain two spaceships.
	\item The game shall be able to load a multiplayer game.
	\item The first spaceship shall be controlled using predefined keys on the keyboard.
	\item The second spaceship shall be controlled using predefined keys on the keyboard.
\end{itemize}

\subsection{Should Haves}
The local co-op multiplayer should meet the following requirements:
\begin{itemize}
	\item The User Interface shall have a menu to select between single or multiplayer games.
	\item The User Interface shall display two different score elements and life elements for different players.
	\item Each spaceship shall have an equal initial movement speed.
	\item Powerups work for individual spaceships.
\end{itemize}

\subsection{Could Haves}
The local co-op multiplayer could meet the following requirements:
\begin{itemize}
	\item The game shall end after one of both players runs out of lives.
	\item The game shall display the winner after the game ends.
	\item The player wins if he/she has the highest score.
\end{itemize}

\subsection{Would/Won't Haves}
The local co-op multiplayer won't meet the following requirements:
\begin{itemize}
	\item Spaceships shall collide.
\end{itemize}