\section{Functional Requirements}

A list of functional requirements which were considered during the planning of the project. Functional requirements describe services or functions a system should deliver to the end user. The requirements are listed using the MoSCoW method. The MoSCoW method is a widely used standard in the industry and involves prioritized requirements. The requirements are categorized in four categories, 'Must', 'Should', 'Could' and 'Would/Won't'. If a 'Must' is not included in the final deliverable, the project is not considered a success.

\subsection{Must Haves}
The Space Invader game must meet the following requirements:
\begin{itemize}
	\item The game shall start when the player presses a predefined  key on the keyboard.
	\item The game shall load a grid of a random amount of enemies in the form of aliens before a new game starts.
	\item The game shall load a player in the form of a spaceship on the bottom of the screen before a new game starts.
	\item The player shall have three lives after a new game has started.
	\item The player shall lose one life when it is hit by an enemy bullet.
	\item The enemies shall move horizontal in between the borders of the game screen, starting in the middle of the screen, from left to right.
	\item The enemies shall start with a movement speed of a predefined amount of pixels per second.
	\item The enemies movement direction shall be reversed upon hitting a border of the game screen.
	\item The standard enemies shall move 10 pixels downwards upon hitting a border of the game screen.
	\item The game shall end if the player's lives are depleted.
	\item The game shall end if the enemies reach the same height as the player.
	\item The player shall be able to move his/her character on a horizontal axis to the left and right using predefined keys.
	\item The player shall be able to shoot bullets on a vertical axis towards the top of the screen using a predefined key.
	\item The enemies shall shoot bullets on a vertical axis towards the bottom of the screen.
	\item An enemy shall disappear if it is hit by a bullet shot by the player.
	\item The game shall show the amount of lives on the top right of the screen.
\end{itemize}

\subsection{Should Haves}
The Space Invader game should meet the following requirements:
\begin{itemize}
	\item The player shall be able to restart the game after the game ends.
	\item The game shall be able to display the overall high score on the screen.
	\item The enemies shall move 4 pixels per second faster upon hitting the border of the game screen.
	\item The game shall load 4 barricades between the enemy and the player before a new game starts.
	\item The barricades shall become damaged after being hit by a bullet.
	\item The bullet shall disappear after hitting a barricade.
	\item The player shall be able to pause the game.
	\item A player shall obtain ten points upon killing an enemy with a bullet.
	\item The game shall load with an initial score of zero points.
	\item The game shall show the total amount of points obtained on the top left of the screen.	
	\item The game shall notify the player on the screen after the game ends.	
	\item The game shall load a new grid of a  random amount of enemies in the form of aliens if all the aliens are killed.
\end{itemize}

\subsection{Could Haves}
The Space Invader game could meet the following requirements:
\begin{itemize}
	\item The game shall have different levels which can be played by the player.
	\item The player shall be able to collect power-ups by killiing an enemy.
	\item The game shall have a power-up which increases shooting speed for five seconds.
	\item The game shall have a power-up which increases movement speed for five seconds.
	\item The game shall play a music track while the game is in progress.
	\item The game shall have sounds effects if a bullet is fired and if a bullet hits an enemy.
	\item The game shall display an explosion effect after an enemy or player is hit by a bullet.
	\item The players movement speed shall increase while moving.
	\item The player shall bounce back upon hitting the border of the screen.
\end{itemize}

\subsection{Would/Won't Haves}
The Space Invader game could meet the following requirements:
\begin{itemize}
	\item The player shall be able to upgrade its spaceship after a wave of enemies.
	\item The player shall be able to interact with the game using the mouse.
\end{itemize}