\section{Sprint 5 Functional Requirements}

A list of functional requirements considered for the implementation of crumbling barricades, boss levels and sound effects using the MoSCoW method described in the previous section.

\subsection{Must Haves}
Sprint 5 must meet the following requirements:
\begin{itemize}
	\item A barricade shall crumble on impact of a bullet.
	\item Bullets shall be able to pass through a partly crumbled barricade. 
	\item A boss shall spawn every n-th level.
	\item A boss shall be a large enemy with a different sprite.
	\item A sound effect shall be played if a unit explodes.
	\item A sound effect shall be played if a player shoots.
\end{itemize}

\subsection{Should Haves}
Sprint 5 should meet the following requirements:
\begin{itemize}
	\item A barricade shall crumble at the location of the impact of the bullet.
	\item A boss shall shoot multiple bullets at once.
	\item A boss shall have multiple lives.
	\item A boss level shall be a separate wave.
	\item A boss shall not move downwards.
\end{itemize}

\subsection{Could Haves}
Sprint 5 could meet the following requirements:
\begin{itemize}
	\item A sound effect shall be played if a new wave occurs.
	\item A barricade shall emit particles on impact of a bullet.
	\item The health of the boss shall be displayed in the User Interface.
\end{itemize}

\subsection{Would/Won't Haves}
Sprint 5 won't meet the following requirements:
\begin{itemize}
	\item A boss shall shoot in different directions.
\end{itemize}
